BACI of biomass change for VOCC source cells

### 2019-09-12 analysis/VOCC/old-rmds/1-biomass-temp-models.Rmd
move old rmds into separate folder

Species
```{r}
species <- params$species

# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Quillback Rockfish"
# species <- "Pacific Ocean Perch"
# species <- "Yelloweye Rockfish"
```

Region 
```{r}
region <- "Both odd year surveys"
# region <- "West Coast Vancouver Island"
#  region <- "West Coast Haida Gwaii"
```

Choose model details
```{r}
#priors <- FALSE
priors <- TRUE

covariates <- "+muddy+any_rock"
# covariates <- ""

# covariates <- "+muddy+mixed+rocky"
# covariates <- "+mixed+rocky"
# covariates <- "+trawled+muddy+rocky+mixed"
# covariates <- "+trawled+mixed+rocky"
# covariates <- "+trawled+mixed"
```

@@

  CTD <- readRDS("../tmb-sensor-explore/data/all-sensor-data-processed.rds")
  data <- dplyr::left_join(data, CTD) %>% 
  mutate(exclude = if_else(do_mlpl>8, 1, 0)) %>% filter(exclude != 1) %>% # added on july 24 after first round of models run...
    filter(year > 2007) # 2007 DO data is flawed

  # scale predictors before filtering to ensure mean and SD are global
  data <- data %>% mutate(raw_depth = depth, depth = log(raw_depth), temp = temperature_c) 
  do_data <- gfranges::scale_predictors(data, predictors = c(quo(depth), quo(temp), quo(do_mlpl)))
       # c(quo(log_depth), quo(mixed), quo(muddy), quo(sandy), quo(rocky), quo(any_rock)))
  data <- do_data %>% mutate(depth = raw_depth) %>% 
    filter(ssid %in% model_ssid) %>% filter(!is.na(do_mlpl))# %>% filter(year != 2016)
```

@@

Run DO sdmTMB model
```{r}
  if (any(names(data) == "adult_density")) {

@@

    starttime1 <- Sys.time()
    adult_biomass_d <- sdmTMB::sdmTMB(data,
      adult_formula,
      time_varying = ~ 0 + do_mlpl_scaled + do_mlpl_scaled2, # + trawled
      time = "year", spde = spde,
      family = tweedie(link = "log"),
      ar1_fields = TRUE,
      include_spatial = TRUE,
      enable_priors = priors,
      control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
      silent = FALSE
    )
    endtime1 <- Sys.time()
    time1 <- round(starttime1 - endtime1)

    saveRDS(adult_biomass_d, 
      file = paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
        ))

@@

    starttime2 <- Sys.time()
    imm_biomass_d <- sdmTMB::sdmTMB(data, 
      imm_formula,
      time_varying = ~ 0 + do_mlpl_scaled + do_mlpl_scaled2, # + trawled
      time = "year", spde = spde,
      family = tweedie(link = "log"),
      ar1_fields = FALSE,
      include_spatial = TRUE,
      enable_priors = priors,
      control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
      silent = FALSE
    )
    endtime2 <- Sys.time()
    time2 <- round(starttime2 - endtime2)

    saveRDS(imm_biomass_d, 
      file = paste0("data/", spp, 
        "/mod-imm-biomass-", spp,"-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
        ))

@@

    total_biomass_d <- sdmTMB::sdmTMB(data,
      dens_formula,
      time_varying = ~ 0 + do_mlpl_scaled + do_mlpl_scaled2, # + trawled
      time = "year", spde = spde,
      family = tweedie(link = "log"),
      ar1_fields = TRUE,
      include_spatial = TRUE,
      enable_priors = priors,
      control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
      silent = FALSE
    )
    endtime3 <- Sys.time()
    time3 <- round(starttime3 - endtime3)

    saveRDS(total_biomass_d, file = paste0("data/", spp, 
      "/model-total-biomass-", spp, "-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
      ))
  }
```

>>>>

Species
```{r}
species <- params$species
# # Species run so far...
species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds

# species <- "Quillback Rockfish"
# species <- "Pacific Ocean Perch"
# species <- "Yelloweye Rockfish"
```

Region 
```{r}
region <- "Both odd year surveys"
 region <- "West Coast Vancouver Island"
 region <- "West Coast Haida Gwaii"
```

Choose model details
```{r}
#priors <- FALSE
priors <- TRUE
covariates <- "+muddy+any_rock"
 # covariates <- ""
# covariates <- "+muddy+mixed+rocky"
# covariates <- "+mixed+rocky"
# covariates <- "+trawled+muddy+rocky+mixed"
# covariates <- "+trawled+mixed+rocky"
# covariates <- "+trawled+mixed"
```

@@

  CTD <- readRDS("../tmb-sensor-explore/data/all-sensor-data-processed.rds")
  data <- dplyr::left_join(data, CTD)

  # scale predictors before filtering to ensure mean and SD are global
  data <- data %>% mutate(raw_depth = depth, depth = log(raw_depth), temp = temperature_c) 
  do_data <- gfranges::scale_predictors(data, predictors = c(quo(depth), quo(temp), quo(do_mlpl)))
       # c(quo(log_depth), quo(mixed), quo(muddy), quo(sandy), quo(rocky), quo(any_rock)))
  data <- do_data %>% mutate(depth = raw_depth) %>% 
    filter(ssid %in% model_ssid) %>% filter(!is.na(temp))# %>% filter(year != 2016)
```

@@

Run temperature sdmTMB model
```{r}
  if (any(names(data) == "adult_density")) {

@@

    starttime1 <- Sys.time()
    adult_biomass_t <- sdmTMB::sdmTMB(data,
      adult_formula,
      time_varying = ~ 0 + temp_scaled + temp_scaled2,
      time = "year", spde = spde,
      family = tweedie(link = "log"),
      ar1_fields = TRUE,
      include_spatial = TRUE,
      enable_priors = priors,
      control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
      silent = FALSE
    )
    endtime1 <- Sys.time()
    time1 <- round(starttime1 - endtime1)

    saveRDS(adult_biomass_t, 
      file = paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
        ))

@@

    starttime2 <- Sys.time()
    imm_biomass_t <- sdmTMB::sdmTMB(data, 
      imm_formula,
      time_varying = ~ 0 + temp_scaled + temp_scaled2,
      time = "year", spde = spde,
      family = tweedie(link = "log"),
      ar1_fields = FALSE,
      include_spatial = TRUE,
      enable_priors = priors,
      control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
      silent = FALSE
    )
    endtime2 <- Sys.time()
    time2 <- round(starttime2 - endtime2)

    saveRDS(imm_biomass_t, 
      file = paste0("data/", spp, 
        "/mod-imm-biomass-", spp,"-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
        ))

@@

    total_biomass_t <- sdmTMB::sdmTMB(data,
      dens_formula,
      time_varying = ~ 0 + temp_scaled + temp_scaled2,
      time = "year", spde = spde,
      family = tweedie(link = "log"),
      ar1_fields = TRUE,
      include_spatial = TRUE,
      enable_priors = priors,
      control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
      silent = FALSE
    )
    endtime3 <- Sys.time()
    time3 <- round(starttime3 - endtime3)

    saveRDS(total_biomass_t, file = paste0("data/", spp, 
      "/model-total-biomass-", spp, "-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
      ))
  }
```

### 2019-09-12 analysis/VOCC/old-rmds/4-vocc-BACI.Rmd
move old rmds into separate folder

### Plot matches
```{r}
ggplot(data, 
#ggplot(filter(data, as.numeric(matchobs) <= 550), 
  aes(y=Y, x=X, shape=as.factor(treat), colour=as.factor(matchobs))) +
  geom_point(alpha=0.4, size = 2) +
  scale_shape_manual(values= c(0, 15)) +
  scale_colour_viridis_d(option="C", guide = FALSE) +
  theme_bw()

>>>>

### Plot matches
```{r}
ggplot(data, 
#ggplot(filter(data, as.numeric(matchobs) <= 550), 
  aes(y=Y, x=X, shape=as.factor(treat), colour=as.factor(matchobs))) +
  geom_point(alpha=0.8, size = 1.5) +
  scale_shape_manual(values= c(0, 15)) +
  scale_colour_viridis_d(option="C", guide = FALSE) +
  theme_bw()
